%______________________________________________________________________________________________________________________

% CV
% Created by Ross Beale

\documentclass[margin,line,a4paper]{resume}
\usepackage{units}
\usepackage{multicol}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large ROSS BEALE}
\begin{resume}

%______________________________________________________________________________________________________________________
	
	% Contact

	\section{\mysidestyle Information}

	\textbf{location:} Reading, Berkshire  
	\hfill 
	\textbf{phone:} +44 796 905 7969	 
	\hfill 
	\textbf{email:} ross@rossbeale.com

%______________________________________________________________________________________________________________________
    	
	% Profile

	\section{\mysidestyle Profile}

	I have a keen interest in developing \textbf{high quality software which solves common problems}. Throughout my education and career, I have utilised my \textbf{consistent, strong work ethos} to enhance my \textbf{expansive skillset}.  I love the field of technology and I strongly feel my \textbf{technical skills}, \textbf{passion} and \textbf{adaptability} can inject both creativity and innovation into any individual or team project.

%______________________________________________________________________________________________________________________
	
	% Education

	\section{\mysidestyle Education}

    	\textbf{University of Reading}, Berkshire, United Kingdom	\hfill		\textbf{ October 2010 -- Present} 
	\vspace{2mm}\\\
    	\textsl{Computer Science BSc}\
	\vspace{2mm}\

    	\begin{list2}
	\item Final Year Project:
	\vspace{1mm}%
		\begin{list3}
			\item \textsl{Mobile Computing and Location Aware Applications}\
		\end{list3}
	\vspace{1mm}%

	\item Notable Achievements:
	\vspace{1mm}%
		\begin{list3}
			\item Averaged a high 2.1 (\textbf{69\%}) throughout both Parts 1 and 2.
			\item Elected \textbf{Course Representative} within the School of Systems Engineering. I highlighted key student issues to staff and actively promoted the actions needed to rectify them.
			\item Worked as a member of the \textbf{Freshers' Week team}, inducting new students to University.
		\end{list3}
    	\end{list2}

	\vspace{-1mm}%

	\addtolength{\linewidth}{7mm}

    	\textbf{Reigate College Sixth Form}, Surrey, United Kingdom		\hfill		\textbf{ September 2007 -- June 2009} 			
	\vspace{2mm}\\
	\vspace{-8mm}%
		\begin{multicols}{2}
			\begin{list2}
        			\item 'A' Levels:
					\begin{list3}
						\item Computing (Grade \textbf{B})
						\item English Language \& Literature (Grade \textbf{B})
						\columnbreak
						\item Psychology (Grade \textbf{B})
					\end{list3}
				\item 'AS' Levels:
					\begin{list3}
						\item Mathematics (Grade \textbf{C})
					\end{list3}
			\end{list2}
		\end{multicols}
	\vspace{-5mm}%

    	\textbf{Woodcote High School}, Surrey, United Kingdom	\hfill		\textbf{ September 2002 -- June 2007} 			\vspace{3mm}\\
	\vspace{1mm}%
	\textbf{10\nicefrac{1}{2} A* -- C Grade GCSE’s} including English Language, English Literature, Mathematics, Double Science, Information Communication \& Technology and Design \& Technology: Graphic Products.	
	\vspace{1mm}

%______________________________________________________________________________________________________________________
	% Skillset
    	\section{\mysidestyle Skillset}

	Mobile platforms; iOS and Android. Web technologies; Ruby (Sinatra and Ruby on Rails), PostgreSQL, PHP \& MySQL, HTML5/CSS3, JavaScript. Server platforms; including AWS and Heroku.

%______________________________________________________________________________________________________________________
    	
	%  Experience

	 \section{\mysidestyle Experience} 

	\textbf{Conjure}, Software Developer  \hfill \textbf{July 2012 -- Present}\\ 
	\vspace{-3mm}\\\vspace{0mm}%
	Worked in a close-knit development team, developing mobile applications for globally recognised brands.  I mainly spent my time preparing in-house projects (such as Mixer and alibi) for launch, by integrating core functionality, patching software and creating launch material - all to a very high standard of quality. Mixer later went on to feature on TechCrunch and in The Guardian.

	\textbf{WHSmith Travel Stores}, Customer Assistant \hfill \textbf{July 2011 -- September 2011}\\ 		
	\vspace{-3mm}\\\vspace{0mm}%
	Working at WHSmith improved my skills in customer service whilst working in a busy, productive and demanding customer-orientated environment, yet maintaining a very polite and positive attitude to customers.

    	\textbf{Tesco PLC}, Customer Assistant  \hfill \textbf{September 2009 -- February 2010}\\ 
	\vspace{-3mm}\\\vspace{0mm}%
	I ensured to maintain a high level of rapport with customers to represent exceptional customer service.

%______________________________________________________________________________________________________________________
	
	% Other

    	\section{\mysidestyle Other}

	\begin{list2}
		\item Created \textbf{UniApp}, a cross-platform mobile application which provides a portal of information for students at the University of Reading. UniApp later became one of the most popular student-developed University mobile applications in the UK.
		\item Co-founded \textbf{Airbyte}, creating digital products and mobile applications.
		\item Guest speaker at \textbf{Social Developer London} (January 2013).
	\end{list2}

%______________________________________________________________________________________________________________________
 	
	% References

	\section{\mysidestyle References}
	
	\textbf{Available upon request.}\vspace{1mm}\\%

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}

%______________________________________________________________________________________________________________________
% EOF